The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with {\em Gaia} Data and Beyond

### 2019-04-24 paper/ms.tex
Add transition par. to Section 3

\section{Coordinate System Offsets I. Measurement Errors} \label{sec:mes_err}

>>>>

\section{Coordinate System Offsets I. Measurement Errors} \label{sec:mes_err}
We consider the first potential source of coordinate system offsets which
would generate the action errors described in Section~\ref{sec:ref_frame}:
errors in the determination of the Galactocentric parameters. Converting from
heliocentric to Galactocentric coordinates relies on these measurements.
Therefore, errors in their values will induce a systematic offset in the
Galactocentric phase-space position of any observed star.
